---
title: "3 Results using Existing Data"
format: 
  html:
    fig-height: 3
editor: source
---

```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(cmdstanr)

source("../../functions/import_data.R")
source("../../functions/prep_data.R")
source("../../functions/compute_summary_stats.R")
source("../../functions/plot_model.R")
source("../../functions/plot_data.R")
source("../../functions/post_functions.R")
source("../../functions/sim_foraging_data.R")

options(mc.cores = 1, digits = 2)

# set global ggplot theme
theme_set(ggthemes::theme_tufte())
```

these are fit by script `fit_all_models.R` and run on our cluster/big-chungus.

We then compute accuracy for each model using script `2_`

# Which model fits best 

We are evaluating using the following datasets:

```{r}
datasets <- c("kristjansson2014plos", "tagu2022cog", "hughes2024rsos")
```

## Prediction Accuracy

Compute chance base-rates for each dataset

- Should these calculations include initial and last selection?

```{r}

baseline <- tibble()

for (dataset in datasets) {
  
  d <- import_data(dataset)
  
  d$stim %>% group_by(person, trial) %>%
    summarise(n = n(), .groups = "drop") -> dn
  
  items <- seq(1, unique(dn$n))
  items_left <- unique(dn$n) - items + 1
  
  n_conditions <- length(levels(d$stim$condition))
  
  d_baseline <- tibble(data = rep(dataset, n_conditions),
                       condition = levels(d$stim$condition),
                       accuracy = rep(mean(1/items_left), n_conditions))
  
  baseline <- bind_rows(baseline, d_baseline)
}

baseline <- bind_rows(baseline %>% mutate(split = "training"),
                      baseline %>% mutate(split = "testing")) %>%
  mutate(model = "baseline")

rm(d, items, items_left)
```

Now get all the pre-computed training/test split accuracies

```{r}
get_acc <- function(dataset) {

  acc <- read_csv(paste0("scratch/post_acc_", dataset, ".csv"),
                  show_col_types = FALSE) %>%
    group_by(split, condition, model, data, .draw) %>%
    summarise(accuracy = median(accuracy), .groups = "drop_last") %>%
    median_hdci(accuracy, .width = c(0.53, 0.97))
  
  return(acc)

}

d_acc <- map_df(datasets, get_acc)

rm(get_acc)
```

```{r}
#| label: compute-all_acc

# combine this with baseline
d_acc %>% #bind_rows(baseline) %>%
  mutate(model = factor(model),
                split = factor(split, levels = c("training", "testing"))) -> d_acc

d_acc %>% ggplot(aes(model, accuracy, colour = condition,
                     ymin = .lower, ymax = .upper)) +
  geom_interval(position = position_dodge(0.1), alpha = 0.5) +
  geom_line(aes(x = as.numeric(as_factor(model)))) +
  ggh4x::facet_grid2(split~data, scales = "free_y") +
  scale_color_viridis_d("dataset - condition") + 
  theme(legend.position = "none")
```

## ELPD? 

# Posterior Densities

```{r}
#| warning: false
#| echo: false

# write a helpful wrapper function

get_plot <- function(d, dataset, modelver) {
  
  m <- readRDS(paste0("scratch/", dataset, "_train_", modelver, ".model"))
  post <- extract_post(m, d)
  plt <- plot_model_fixed(post)
  
  return(plt)
  
}
```

## kristjansson2014plos

```{r}

dataset <- "kristjansson2014plos"
d <- import_data(dataset)

get_plot(d, "kristjansson2014plos", "1_0") / 
  get_plot(d, "kristjansson2014plos", "1_1")  / 
  get_plot(d, "kristjansson2014plos", "1_2") + 
  plot_layout(guides = "collect")

```

## hughes2024rsos

```{r}

dataset <- "hughes2024rsos"
d <- import_data(dataset)

get_plot(d, "hughes2024rsos", "1_0") / 
  get_plot(d, "hughes2024rsos", "1_1")  / 
  get_plot(d, "hughes2024rsos", "1_2") + 
  plot_layout(guides = "collect")

```

# Posterior Predictions

Compare run statistics and inter-item-selection-vectors

## Run Statistics

```{r}
#| fig-height: 5

rl10 <- read_csv("scratch/run_statistics1_0.csv", 
                 show_col_types = FALSE) %>% mutate(model = "FoMo 1.0")
rl11 <- read_csv("scratch/run_statistics1_1.csv", 
                 show_col_types = FALSE) %>% mutate(model = "FoMo 1.1")
rl12 <- read_csv("scratch/run_statistics1_2.csv", 
                 show_col_types = FALSE) %>% mutate(model = "FoMo 1.2")

bind_rows(rl10, rl11, rl12) %>%
 ggplot(aes(observed, predicted, colour = condition))  +
  geom_point() + 
  geom_abline(linetype = 2) + 
  facet_grid(model ~ dataset) + 
  coord_fixed() +
  theme(legend.position = "none")
```


## Inter-Item Selection Distance

```{r}
#| fig-height: 5
#|

iisv <- bind_rows(
  read_csv("scratch/iisv_statistics1_0.csv") %>% mutate(model = "1.0"),
  read_csv("scratch/iisv_statistics1_1.csv") %>% mutate(model = "1.1"))

iisv %>%
  group_by(condition, found, x, model, dataset) %>%
  summarise(d2 = mean(d2)) %>%
 ggplot(aes(found, y = d2, linetype = x, group = interaction(x, condition)))  +
  geom_path(aes(colour = condition)) + 
  facet_grid(dataset ~ model) +
  theme(legend.title = element_blank()) + 
  scale_y_log10()
```

## Inter-Item Selection Relative Directions

```{r}

iisv %>%
  ggplot(aes(psi, linetype = x, group = interaction(x, condition)))  +
  geom_density(aes(colour = condition)) + 
  facet_grid(dataset ~ model) +
  theme(legend.title = element_blank()) + 
  scale_y_log10()
```

## Inter-Item Selection Absolute Directions

