---
title: "4: A model report"
format: 
  html:
    fig-height: 3
editor: source
---

```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(cmdstanr)

source("../../functions/import_data.R")
source("../../functions/prep_data.R")
source("../../functions/compute_summary_stats.R")
source("../../functions/plot_model.R")
source("../../functions/plot_data.R")
source("../../functions/post_functions.R")
source("../../functions/sim_foraging_data.R")

options(mc.cores = 1, digits = 2)

# set global ggplot theme
theme_set(ggthemes::theme_tufte())
```

these are fit by script `fit_all_models.R` and run on our cluster/big-chungus.

We then compute accuracy for each model using script `2_`

Here we provide more in depth analysis on how well a particular model fits a given dataset


```{r}
model_ver <- "1_2"
dataset   <- "tagu2022cog"
```


```{r}
# read in data
d <- import_data(dataset)

# read in model and predictions for test data
m <- read_rds(paste0("scratch/", dataset, "_train_", model_ver, ".model"))
t <- read_rds(paste0("scratch/", dataset, "_test_", model_ver, ".model"))
```

# How well does the model fit?

## Prediction Accuracy

Compute chance base-rates for each dataset
```{r}
d$stim %>% group_by(person, trial) %>%
  summarise(n = n(), .groups = "drop") -> dn
  
items <- seq(1, unique(dn$n))
items_left <- unique(dn$n) - items + 1
  
n_conditions <- length(levels(d$stim$condition))
  
baseline <- tibble(found = 1:unique(dn$n),
                   accuracy = (1/items_left))
  
rm(items, items_left)
```


```{r}
#| label: compute-all_acc
#| cache: true

pred <- summarise_postpred(list(training = m, testing = t), d, 
                                 get_sim = FALSE, draw_sample_frac=0.25)
acc <- compute_acc(pred$acc)

acc %>% ggplot(aes(found, accuracy, fill = condition, colour = condition,
                     ymin = .lower, ymax = .upper,
                  group = interaction(condition, .width))) +
  geom_lineribbon(alpha = 0.5) +
  facet_grid(.~split) +
  scale_color_viridis_d() + 
  scale_fill_viridis_d()
```

## ELPD? 

# Model checking

Did the mcmc sampling work ok? 

```{r}

# diagnostic checks
# m$diagnostic_summary()
# 
# traceplots
 bayesplot::mcmc_trace(m$draws(),
                      pars = c("b_a[1]", "b_a[2]", "b_stick[1]", "b_stick[2]", 
                                "rho_delta[1]", "rho_delta[2]"),  #, "rho_psi[1]", "rho_psi[2]"
                      facet_args = list(nrow = 2))
```


# Posterior Densities

```{r}
#| warning: false
#| echo: false


post <- extract_post(m, d)
plot_model_fixed(post)
```

<!-- # Posterior Predictions -->

<!-- Compare run statistics and inter-item-selection-vectors -->

<!-- ## Run Statistics -->

<!-- ```{r} -->
<!-- rl10 <- read_csv("scratch/run_statistics1_0.csv",  -->
<!--                  show_col_types = FALSE) %>% mutate(model = "FoMo 1.0") -->
<!-- rl11 <- read_csv("scratch/run_statistics1_1.csv",  -->
<!--                  show_col_types = FALSE) %>% mutate(model = "FoMo 1.1") -->

<!-- bind_rows(rl10, rl11) %>% -->
<!--  ggplot(aes(observed, predicted, colour = condition))  + -->
<!--   geom_point() +  -->
<!--   geom_abline(linetype = 2) +  -->
<!--   facet_wrap(model ~ dataset) -->
<!-- ``` -->


<!-- ## Inter-Item Selection Distance -->

<!-- ### FoMo 1.0 -->

<!-- ```{r} -->
<!-- iisv <- read_csv("scratch/iisv_statistics1_0.csv") -->

<!-- iisv %>% -->
<!--  ggplot(aes(found, y = d2, ymin = .lower, ymax = .upper, fill = x, group = interaction(x, .width)))  + -->
<!--   geom_path(aes(colour = x)) +  -->
<!--   geom_ribbon(alpha = 0.33) +  -->
<!--   facet_wrap(condition ~ dataset) + -->
<!--   theme(legend.title = element_blank()) +  -->
<!--   scale_y_log10() -->
<!-- ``` -->


<!-- ### FoMo 1.1 -->

<!-- ```{r} -->
<!-- iisv <- read_csv("scratch/iisv_statistics1_1.csv") -->

<!-- iisv %>% -->
<!--  ggplot(aes(found, y = d2, ymin = .lower, ymax = .upper, fill = x, group = interaction(x, .width)))  + -->
<!--   geom_path(aes(colour = x)) +  -->
<!--   geom_ribbon(alpha = 0.33) +  -->
<!--   facet_wrap(condition ~ dataset) + -->
<!--   theme(legend.title = element_blank()) +  -->
<!--   scale_y_log10() -->
<!-- ``` -->


<!-- ### FoMo 1.2 -->

<!-- ```{r} -->
<!-- iisv <- read_csv("scratch/iisv_statistics1_2.csv") -->

<!-- iisv %>% -->
<!--  ggplot(aes(found, y = d2, ymin = .lower, ymax = .upper, fill = x, group = interaction(x, .width)))  + -->
<!--   geom_path(aes(colour = x)) +  -->
<!--   geom_ribbon(alpha = 0.33) +  -->
<!--   facet_wrap(condition ~ dataset) + -->
<!--   theme(legend.title = element_blank()) +  -->
<!--   scale_y_log10() -->
<!-- ``` -->
