---
title: "Plot model example"
author: "Anna Hughes & Alasdair Clarke"
format: html
editor: visual
---


This file takes a previously fitted model (see 1_fit_models) and creates a load of plots giving an overview of how well the model fits the data.


- accuracy plot
- run statistics plots (observed vs. predicted)
- posterior density plots (including theta plots for relevant model versions)

```{r, echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse)
library(cmdstanr)
library(patchwork)
library(tidybayes)

source("../functions/import_data.R")
source("../functions/compute_summary_stats.R")
source("../functions/post_functions.R")
source("../functions/plot_model.R")

options(mc.cores = 1, digits = 2)

# set global ggplot theme
theme_set(theme_bw())

```

# Set your dataset and model version here

```{r}

model_ver <- "1_0"
dataset <- "kristjansson2014plos"
free_or_fixed <- "v" # "v" for free, "f" for fixed

```

```{r, echo = FALSE}

# read in data
d <- import_data(dataset)

sf <- "1_fit_models/scratch"
folder <- paste0(sf, "/post/", dataset, "/")

```

# Accuracy plot

```{r, echo = FALSE}

pred <- readRDS(paste0(folder, "pred_", model_ver, ".rds"))

pred$itemwise %>% 
  group_by(condition, found, .draw, person) %>%
  summarise(person_acc = mean(model_correct), .groups = "drop_last") %>%
  summarise(accuracy = mean(person_acc), .groups = "drop_last") -> acc

plt_acc <- plot_model_accuracy(acc)

plt_acc

rm(acc)

```

# Run statistics plots & correlations

```{r, echo = FALSE, message = FALSE}

trl_stats <- read_csv(paste0("1_fit_models/scratch/post/", dataset, "/run_statistics.csv")) %>%
  pivot_longer(starts_with(free_or_fixed), names_to = "model_version", values_to = "predicted")

# reorder factor levels for plotting
trl_stats %>% 
  filter(.draw == 1, model_version == paste0(free_or_fixed, model_ver)) %>%
  mutate(statistic = fct_recode(statistic, 
                                `number of runs` = "num_runs", 
                                `max(run length)` = "max_run_length",
                                pao = "mean_pao",
                                `best r`  = "mean_bestr",
                                `mean intersections` = "mean_int"),
         statistic = fct_relevel(statistic, 
                                 "number of runs", "max(run length)", "pao")) -> trl_stats

ggplot(trl_stats, aes(predicted, observed, colour = condition)) + 
  geom_point() + 
  geom_abline(linetype = 2) + 
  facet_wrap( ~ statistic, nrow = 2, scales = "free") +
  theme(legend.position = "none") -> plt_runs

plt_runs

comp_r <- function(condition, statistic, model_version, trl_stats) {
  
  t <- filter(trl_stats, 
              {{condition}} == condition,
              {{statistic}} == statistic, 
              {{model_version}} == model_version)
  
  r <- cor.test(t$observed, t$predicted)$estimate
  
  reg_model <- summary(lm(observed ~ predicted, t))$coefficients
  
  return(tibble(condition = condition,
                statistic = statistic,
                model_version = model_version,
                r = r,
                b = reg_model["predicted",1],
                a = reg_model["(Intercept)",1]))
}

trl_stats %>% modelr::data_grid(condition, statistic, model_version) -> to_test

pmap_df(to_test, comp_r, trl_stats = trl_stats) %>%
  knitr::kable()

```

# Posterior densities

```{r, echo = FALSE}

m <- readRDS(paste0("1_fit_models/scratch/models/", dataset, "/fit/", model_ver, ".model"))
post <- extract_post(m, d)
post_plt <- plot_model_fixed(post)
post_plt

post_theta <- plot_model_theta(post, nrow = 1)
post_theta

```