---
title: "3 Results using Existing Data"
format: 
  html:
    fig-height: 3
editor: source
---

```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(cmdstanr)

source("../functions/import_data.R")
source("../functions/prep_data.R")
source("../functions/compute_summary_stats.R")
source("../functions/plot_model.R")
source("../functions/plot_data.R")
source("../functions/post_functions.R")
source("../functions/sim_foraging_data.R")

options(mc.cores = 1, digits = 2)

# set global ggplot theme
theme_set(ggthemes::theme_tufte())
```


See the `1_fit_models` folder for scripts that pre-compute everything

```{r}
sf <- "1_fit_models/scratch"
```


# Which model fits best 

We are evaluating using the following datasets:

```{r}
datasets <- c("kristjansson2014plos", "tagu2022cog", "hughes2024rsos") #,   "clarke2022qjep
```

## Overall Prediction Accuracy

```{r}
for (ds in datasets) {
  plt <- plot_models_accuracy(ds, scratch_folder = sf) + theme_bw() + ggtitle(ds)
  print(plt)
}
```

The improvements in overall accuracy appear modest at best. 

## Per-Person Prediction Accuracy

However, we can see a larger improvement if we compare how well models do at predicting individuals.

```{r}
v1 <- "1_0"
v2 <- "1_3"


for (ds in datasets) {
  plt <- plot_model_accuracy_comparison(ds, v1, v2, scratch_folder = sf) 
  print(plt)
}
```

## Accuracy throughout a trial

For model 1.3? 

```{r}
for (ds in datasets) {
  folder <- paste0(sf, "/post/", ds, "/")
  pred <- readRDS(paste0(folder, "pred_1_3.rds"))
  
  pred$itemwise %>% 
    group_by(condition, found, .draw, person) %>%
    summarise(person_acc = mean(model_correct), .groups = "drop_last") %>%
    summarise(accuracy = mean(person_acc), .groups = "drop_last") -> acc
  
  plt_acc <- plot_model_accuracy(acc)
  print(plt_acc)
}
```


# Posterior Density 


```{r}

model_ver <- "1_3"
```

## Main parameters

```{r}


for (ds in datasets) {
  folder <- paste0(sf, "/models/", ds, "/fit/")
  m <- readRDS(paste0(folder, model_ver, ".model"))
  d <- import_data(ds)
  post <- extract_post(m, d)
  post_plt <- plot_model_fixed(post) + ggtitle(ds)
  print(post_plt)
}


```

## Directional parameters


```{r}
for (ds in datasets) {
  folder <- paste0(sf, "/models/", ds, "/fit/")
  m <- readRDS(paste0(folder, model_ver, ".model"))
  d <- import_data(ds)
  post <- extract_post(m, d)
  plt <- plot_model_theta(post, nrow = 1) + ggtitle(ds)
  print(plt)
}
```





